\section{Introduction}
Content and services which are offered for free on the Internet are sometimes monetized through online advertisements. This relies on the implicit understanding that the viewers who consume free content do so at the cost of viewing ads. However, recent times have seen the  rise of ad blockers that control the display of  advertisements on websites. These adblockers rely on  a list of filters for blocking or allowing advertisements.The lists can be categorized into whitelists and blacklists. Blacklists contain rules for blocking advertisements whereas whitelist acts as exception for the rules that are in the blacklists.
In 2011 adblock plus started monetization of the whitelist by launching what is known was an "Acceptable ads" program.As a part of the acceptable ads program adblock plus proposed  that ads  displayed on a page have to adhere to. A publisher adhering to this crtieria can pay a fee to adblock plus and get themselves whitelisted. It is known that the e-commerce and advertising giants like Amazon, Google and Microsoft paid an undisclosed sum to adblock plus to get themselves whitelisted.

While the number of users of adblock plus continues to grow, on the other hand the number of filters added to the whitelist has also grown over the years.
<Insert fig>, indicates the growth of whitelist since 2011. Unsurprisingly, one can see an increasing trend in the number of ads allowed by adblock plus. This raises
the following questions.
\begin{itemize}
\item [Q1.] Does Adblock Plus allow ads even if they do not satisfy the four criteria ?
\item [Q2.] Does adblock Plus block ads even if they satisfy the four criteria?
\item [Q3.] As more sites are added to the whitelist when can adblock plus be deemed in-effective?
\end{itemize}

We attempt to answer Q1 and Q2 in our project by performing experiments on various websites.
\subsection{Proposed Approach}
In this project we propose to analyze, what  constitutes an acceptable advertisement. We plan to crawl web pages from different sources and analyze them. Additionally, we plan to investigate machine learning as a tool that would aid us in the analysis of the web pages and aid in discriminating between acceptable and unacceptable ads. In particular, we attempt to see if we can discover any patterns from  un-acceptable ads and see if those patterns could  be used to refine the criteria for acceptable ads.

